% Created 2023-08-15 二 20:56
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{yang}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={yang},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{Learning Org Mode}
\label{sec:orgff98b35}

\subsection{Basic Setup and Navigation}
\label{sec:org0b418b2}
\begin{itemize}
\item Install Emacs.
\item Open a file with .org extension.
\item Move the cursor, scroll, open, and save files.
\end{itemize}

\subsection{Headings and Outlining}
\label{sec:org5b74e0e}
\begin{itemize}
\item Create hierarchical structure with asterisks.
\item Experiment with different levels of headings.
\item Use `Tab` to collapse/expand subtrees.
\end{itemize}

\subsection{Creating Lists and Tables}
\label{sec:org2b38e9a}
\begin{itemize}
\item Create bullet and numbered lists.
\item Create tables using | and -.
\end{itemize}

\subsection{Text Formatting}
\label{sec:org8787cbc}
\begin{itemize}
\item Bold: \textbf{bold}
\item Italic: \emph{italic}
\item Code: \texttt{code}
\end{itemize}

\subsection{Links and References}
\label{sec:orgaab3ae6}
\begin{itemize}
\item Internal links: link
\item External links: [Google](\url{https://www.google.com})
\end{itemize}

\subsection{{\bfseries\sffamily TODO} Lists and Checkboxes}
\label{sec:org301e6fe}
\begin{itemize}
\item TODO keywords: TODO, DONE
\item Tasks: - [ ] Task 1, - [X] Task 2
\end{itemize}

\subsection{Tags and Properties}
\label{sec:orge7a0236}
\begin{itemize}
\item Tags: :tag1: :tag2:
\item Properties: :PROPERTY: value
\end{itemize}

\subsection{Clocking and Time Tracking}
\label{sec:orgc89dad5}
\begin{itemize}
\item Clock in: C-c C-x C-i
\item Clock out: C-c C-x C-o
\end{itemize}

\subsection{Agenda and Planning}
\label{sec:org7e87a33}
\begin{itemize}
\item Agenda view: C-c a a
\item SCHEDULED: \textit{<2023-08-15 二>}
\item DEADLINE: \textit{<2023-08-31 四>}
\end{itemize}

\subsection{Exporting and Publishing}
\label{sec:orga149ac8}
\begin{itemize}
\item Export to HTML: C-c C-e HTML
\end{itemize}

\subsection{Customization and Advanced Features}
\label{sec:org3e0a6cb}
\begin{itemize}
\item Customize using M-x customize-group org
\item Capturing templates, custom agenda views, etc.
\end{itemize}

\subsection{Practice and Community Resources}
\label{sec:orgbb77b67}
\begin{itemize}
\item Organize tasks and notes.
\item Visit Org Mode manual: C-h i m Org RET
\item Join Org Mode community forums.
\end{itemize}
\end{document}
